%% awesome-resume.tex
%% Copyright 2026 Andre A Alves
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
%
% The Current Maintainer of this work is Andre A Alves.
%
% This work consists of all files listed in latex/manifest.txt.
%
% Compile from the samples/ directory with TEXINPUTS pointing at latex/:
%   TEXINPUTS=../latex//: lualatex awesome-resume.tex
\documentclass[theme=awesome-resume,10pt]{andre-cv}

\setmainfont{Source Sans 3}
\setsansfont{Source Sans 3}
\setmonofont{Source Sans 3}

\SetName{Henry Jones Jr.}
\SetTown{Bedford, Connecticut, USA}
\SetPhone{203 555 0198}
\SetEmail{indyjones@marshall.edu}
\SetLinkedIn{indy-jones}
\SetGithub{indy-jones}
\SetHomepage{www.marshall.edu/indyjones}

\begin{document}

\DisplayModernHeader
  {Archaeologist \textbullet\ Professor \textbullet\ Explorer}
  {``Fortune and glory, kid. Fortune and glory.''}

\section{Experience}
\cventry[
  dates    = {1936 -- Present},
  title    = {Professor of Archaeology},
  org      = {Marshall College},
  location = {Bedford, Connecticut},
]{\cvitemize{
  \item Lectures on theories of archaeology, methods of excavation, and history of ancient civilizations.
  \item Supervises graduate students in their fieldwork and thesis preparation.
  \item Conducts and publishes research on various archaeological finds.
  \item Organizes and leads summer archaeological expeditions for students and researchers.
}}
\cventry[
  dates    = {1920 -- Present},
  title    = {Archaeologist and Explorer},
  org      = {Freelance},
  location = {Global},
]{\cvitemize{
  \item Conducted numerous archaeological expeditions across South America, Asia, Africa, and Europe.
  \item Recovered and preserved iconic artifacts such as the Ark of the Covenant and the Holy Grail.
  \item Collaborated with museums worldwide to ensure safe and ethical display of artifacts.
  \item Navigated complex political and environmental terrains to access and excavate sites.
}}

\section{Education}
\cventry[
  dates    = {1922},
  title    = {Ph.D.\ in Archaeology},
  org      = {University of Chicago},
  location = {Chicago, Illinois},
]{\cvitemize{
  \item Dissertation: \emph{The Influence of Ritualistic Symbolism in Ancient Mayan Artifacts}.
  \item Conducted extensive field research in Central America as part of doctoral studies.
}}
\cventry[
  dates    = {1916},
  title    = {Bachelor of Arts in European History},
  org      = {Princeton University},
  location = {Princeton, New Jersey},
]{\cvitemize{
  \item Graduated with honors, focusing on ancient European civilizations and their languages.
}}

\section{Skills}
\cvitem{Languages}{English, German, Ancient Greek, Latin, Arabic}
\cvitem{Expertise}{Field excavation, artifact authentication, ancient languages, archival research}
\cvitem{Other}{Whip proficiency, motorcycle operation, combat archaeology}

\section{Professional Affiliations}
\cvitem{Member}{American Society of Archaeologists}
\cvitem{Founding Member}{International Council of Ancient Monument Preservation}

\end{document}
