%% classic-resume.tex
%% Copyright 2026 Andre A Alves
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
%
% The Current Maintainer of this work is Andre A Alves.
%
% This work consists of all files listed in latex/manifest.txt.
%
% Compile from the samples/ directory with TEXINPUTS pointing at latex/:
%   TEXINPUTS=../latex//: lualatex classic-resume.tex
\documentclass[theme=classic-resume,10pt]{andre-cv}

\setmainfont{Source Sans 3}
\setsansfont{Source Sans 3}
\setmonofont{Source Sans 3}

\SetName{Henry Jones Jr.}
\SetTown{Bedford, Connecticut, USA}
\SetPhone{203 555 0198}
\SetEmail{indyjones@marshall.edu}
\SetLinkedIn{indy-jones}
\SetGithub{indy-jones}
\SetHomepage{www.marshall.edu/indyjones}

\begin{document}

\DisplayClassicHeader{Resume}{Archaeologist and Professor}

\ClassicMeta{\DisplayTown}{\textbf{Status:} Professor of Archaeology}
\ClassicMeta{\DisplayHomepage}{\textbf{Fields:} Archaeology, Field Research, Ancient History}
\ClassicMeta{\DisplayEmail}{\textbf{Languages:} English, German, Ancient Greek, Latin}
\ClassicMeta{\DisplayPhone}{\textbf{Activities:} Museum Curation, Expedition Leadership}
\ClassicMetaRule

\section{Summary}
Archaeologist with long-running teaching, fieldwork, and museum collaboration experience. Focused on ancient civilizations, artifact authentication, and the ethical preservation of historical objects.\\

\section{Experience}
\cventry[
  dates    = {1936 -- Present},
  title    = {Professor of Archaeology},
  org      = {Marshall College},
  location = {Bedford, Connecticut},
]{\cvitemize{
  \item Lectures on theories of archaeology, methods of excavation, and history of ancient civilizations.
  \item Supervises graduate students in fieldwork and thesis preparation.
  \item Conducts and publishes research on archaeological finds and their historical implications.
}}
\cventry[
  dates    = {1920 -- Present},
  title    = {Archaeologist and Explorer},
  org      = {Freelance},
  location = {Global},
]{\cvitemize{
  \item Conducted archaeological expeditions across South America, Asia, Africa, and Europe.
  \item Recovered and preserved iconic artifacts for museum and academic partners.
  \item Navigated complex political and environmental terrains to access and excavate sites.
}}

\section{Education}
\cventry[
  dates    = {1922},
  title    = {Ph.D.\ in Archaeology},
  org      = {University of Chicago},
  location = {Chicago, Illinois},
]{\cvitemize{
  \item Dissertation: \emph{The Influence of Ritualistic Symbolism in Ancient Mayan Artifacts}.
  \item Conducted extensive field research in Central America as part of doctoral studies.
}}
\cventry[
  dates    = {1916},
  title    = {Bachelor of Arts in European History},
  org      = {Princeton University},
  location = {Princeton, New Jersey},
]{\cvitemize{
  \item Graduated with honors, focusing on ancient European civilizations and their languages.
}}

\section{Skills}
\cvitem{Expertise}{Field excavation, artifact authentication, archival research}
\cvitem{Tools}{Surveying equipment, archival catalogues, museum preservation workflows}
\cvitem{Other}{Expedition planning, grant reporting, public lectures}

\end{document}
